Illumination Dependency in Dynamic Laser Speckle Analysis

### 2020-02-13 article/article_1.tex
unificando o texto

\documentclass[review]{elsarticle}
\usepackage{comment}
\usepackage{url}
%
\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}

\usepackage[ruled]{algorithm2e}

%\usepackage{lineno}
%\modulolinenumbers[5]

@@

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Study of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{Fernando Pujaico Rivera}
\author{Roberto Alves Braga Jr.}

\address{University Federal of Lavras, Lavras, Brazil}
\fntext[myfootnote2]{201518201@posgrad.ufla.br}
\fntext[myfootnote1]{robertobraga@deg.ufla.br }
%

\begin{abstract}
In this article we show an analysis of how the frequency bands 
influence in the light independence of the speckle index value in a dynamic laser speckle analysis. 
Specifically, 
we studied temporal speckle deviation 
index influenced by the use of three different frequency bands of the speckle signal. 
Finally, it was shown how signals with high frequency components return values with greater illumination level independence.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Dynamic laser speckle is a phenomenon that is used to monitor changes in laser illuminated samples, and it can be measured by multiple indexes \cite{BSLTLBOOK}. The indexes are associated to the level of changes and could be expressed by numerical and or graphical outcomes that can be affected by filtering action during the image processing \cite{RIVERA2017144}. As an example, we have  the $AVD$ \cite{avd} and 
$IM$ \cite{ARIZAGA1999163} indexes, that filter
the information present in the history of the speckle images like a first order high pass filter with a cut-off in the middle
of the normalized frequency band. 
For this reason, it is important to analyze how
the chosen frequency band alters the result of selected index.
By other side, there is still a limitation to make speckle analysis in the presence of non homogeneous illumination, because
the most of biospeckle indexes are influenced in their values
by the use of an specific illumination level \cite{REIS2016}.
The illumination level can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or a very irregular surface present in a kefir \cite{kefir}. 
It can also vary in accordance with the moisture present in the seed \cite{CARDOSO2011} due to the penetration of the light in the sample, or even when the color of the sample vary such as in the interface of cancer and normal tissues \cite{BCB+:12a}. And that is the reason to a continuous search for an adequate index, despite the fact there are many of them present in literature \cite{BSLTLBOOK}, but still without a solution to the independence of light intensity. 
The movement toward the portable equipment \cite{Bra:17}, reinforce the need to search the methods and its relation with the illumination. 
Thus, the present work aimed to establish a relation between the frequency band used
and the speckle index; particularly in the dependence of
the temporal speckle deviation matrix \cite{Nothdurft:05} with the illumination level.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System description}
\label{sec:description}

\subsection{Data packages of ink drying}
\label{sec:descriptionink}
Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
a red laser was pointed to a layer of ink drying monitored by a digital camera;
the images are collected receiving two different illumination levels, 
because the neutral density lens partially covers partially the laser beam \cite{REIS2016}.
The images were placed in data packages and
are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with the two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of ink drying.}
\label{fig:system}
\end{figure}
In each image of the packages were selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with red lines in the Fig. \ref{fig:regions}; thus, 
in the right side of the Fig. \ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens.
Thus, the right side has low illumination, and
the left side has a high illumination.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}
%\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\

\subsection{Data packages of a steady state paper}
\label{sec:descriptionpaper}
The test over a steady state paper has a similar configuration that seen in
the Fig. \ref{fig:system} with the absence of 
the neutral density lens. 
The phenomenon observed was the speckle signal  variation associated with  the speckle response of material, 
the experimental setup of the camera, the resolution of the images and also to the mechanical noise; 
so that it was collected one data package sampled with a frequency of $F_s=$ 10 hertz, being 
collected in total $N=129$ images of 640$\times$480 pixels.
The Fig. \ref{fig:meanpaper} represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}; thus, it is easy to see how the
illumination level of laser over the paper has an elliptical form being highest 
close to the top of the image.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall.eps}
\caption{Light intensity distribution in the paper piece test with highest illumination presented by red pixels and lowest by blue pixels.}
\label{fig:meanpaper}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical analysis}
\label{sec:analysis}

The sampling frequency used in the analysis of each test, 
it was selected  trying to achieve the best speed of sampling to observe each phenomenon. 
The purpose of these two tests is to observe the behavior of the indices in two cases; 
one with an activity homogeneous level in space and time, and another with a heterogeneous activity.
Thus, given that the paper activity test and the ink drying test are independent events, 
without comparison between them self, your sampling frequencies are different,
and selected according to the best behavior of the curves, 
being more appropriate higher sampling frequencies for the ink drying test.

\subsection{Data package filtering in three frequency band}
\label{subsec:firfilters}
Each data package or sub package ($P_T$) went through of a filter bank with 4 outputs  having each
one, a different type of processing, the first output is trivial because it
lets to pass the information freely, this package is called of $P_T$, whilst the other 3 outcomes
return  signals filtered by a frequency band; thus, 
we have the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
the band between $[\frac{1}{3},\frac{2}{3}]\frac{F_s}{2}$ (intermediate frequencies) and
the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies); obtaining at end, the packages 
$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in the  Fig. \ref{fig:firfilters}.
The filtered packages of images were carried out using cascades
of two low-pass Finite Impulse Response ($FIR$) filters of order $32$, so that
the sum of signals $P_X+P_Y+P_Z=P_T$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.55\columnwidth]{firfilters.eps}
\caption{Filtering of data packages.}
\label{fig:firfilters}
\end{figure}

\subsection{Temporal speckle deviation matrix}
\label{subsec:deviation}
The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05},
used to compare the results, it was obtained from the $N$ images of the data package $P$.
We designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, 
being $k$ an integer index that indicates that, it is in use the $k$-th image $\mathbf{I}$ in the package.
Thus, to get
% the value $\bar{\sigma}$, it is necessary to get 
the matrix $\sigma$ is used the Equation \ref{eq:cont2}, 
\begin{equation}\label{eq:cont2}
\sigma  = \sqrt{ \frac{1}{N} \sum_{k=1}^{N} (\mathbf{I}_{k}-\mu)^2  },
\end{equation}
being that, the matrix $\mu$ can be calculated as, 
\begin{equation}\label{eq:cont1}
\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k}.
\end{equation}
In these last two equations, all the operations are matricial, 
so that each element (aka pixel) $\mathbf{I}_{k}(i)$ in the matrix $\mathbf{I}_{k}$
should be processed with your  counterpart $\mathbf{I}_{k+1}(i)$ in the matrix $\mathbf{I}_{k+1}$.

Aditionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
of all elements in the matrix $\sigma$, being $<.>$ the mean spatial operator.
%And $\sigma_p$ as any value of an element in  $\sigma$.

@@

The Fujii matrix \cite{Fujii:87} is obtained from the $N$ images in the data package $P$.
Similarly to the Section \ref{subsec:deviation}, 
we designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$.
Thus, to get the Fujii matrix is used the Equation \ref{eq:contFujii2}, 
\begin{equation}\label{eq:contFujii2}
Fujii  = \frac{1}{N-1} \sum_{k=1}^{N-1} \frac{|\mathbf{I}_{k}-\mathbf{I}_{k+1}|}{\mathbf{I}_{k}+\mathbf{I}_{k+1}}.
\end{equation} 
The  Fujii matrix mean value can be defined as $\overline{Fujii}=<Fujii>$, the mean value
of all elements in the $Fujii$ matrix.

The Fujii method represents the attempt to eliminate 
the dependence on illumination level, in a speckle index.
For this purpose, the method define the index as the mean value of the  first order high pass FIR filter, 
$\mathbf{I}_{k}-\mathbf{I}_{k+1}$, similarly to the  $AVD$ index \cite{avd};
but in the Fujii method the values are corrected using an approximation of the intensity mean value, $\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
This calculation aspect is the strong point of the method,
because the method assumes that the increase in the speckle 
light dynamic range ($\mathbf{I}_{k}-\mathbf{I}_{k+1}$) 
will be linear in proportion with the increase in laser light ($\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$).
This means that the method already uses high frequency components, 
of the speckle signal, 
and discards those of low frequency, 
in addition to attempting to correct or  normalize the index values;
and it is for these characteristics that it shows an acceptable performance,
to eliminate or decrease the dependence of the index with the laser intensity level.

Additionally, it was defined the matrix $Fujii_{\alpha}$, 
as the index of the filtered version of package $P$ to the frequency band $\alpha$, following the Equation \ref{eq:contFujii3}.
\begin{equation}\label{eq:contFujii3}
Fujii_{\alpha}  = \frac{1}{N-1} \sum_{k=1}^{N-1} \frac{|\mathbf{(I_{\alpha})}_{k}-\mathbf{(I_{\alpha})}_{k+1}|}{\mathbf{I}_{k}+\mathbf{I}_{k+1}}.
\end{equation}
It is important to highlight that the numerator of the last equation, 
use the signal in the matrices $\mathbf{(I_{\alpha})}_{k}$, that are filtered versions in the frequency band $\alpha$,
of the matrix $\mathbf{I}_{k}$. 
By other side, the denominator use the signal $\mathbf{I}_{k}$ which has the complete frequency band.
This modification was implemented because the numerator, in the calculus, 
represents or try be the mean value of speckle light intensity, 
and it value tend to zero in frequency bands without 0 hertz components.

\subsection{Datapack processing in the ink drying test}
\label{subsec:numprocink}

We have in the ink drying regions
two levels of illumination; thus, we  separated each package in two sub package
(high and low illumination), representing each one of the regions shown in the Fig. \ref{fig:regions}.
These sub-packages were filtered,
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, that was used to obtain
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data packages.}
\label{fig:filtering}
\end{figure}
the temporal speckle deviation matrix and the 
temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$.

\subsection{Statistical analysis of relation between the matrices $\sigma$ and $\mu$}
\label{subsec:statistical}
We define $\sigma_i$ and $\mu_i$
as the values in the $i-th$ position in the $\sigma$  
and $\mu$ matrices, respectively; we also defined $\mu_p$
as any element value in  $\mu$.
And we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
as the set of all $\sigma_i$  values given that $\mu_i\equiv\mu_p$.
Then, we obtained the vectors $L_p$, $\sigma_p$ and
$e_p$ using all the $\mu_p$ values, according to:
\begin{itemize}
 \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  being $L_p(\mu_p)$ the number of elements
 in the set $S_{\mu_p}$ and $card(.)$ the cardinality function operator.
 \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, being $\sigma_p(\mu_p)$
 the mean value of elements in the set $S_{\mu_p}$ with $mean(.)$ representing the mean value function operator.
 \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, being $\e_p(\mu_p)$
 the standard  deviation value of elements in the set $S_{\mu_p}$ with $std(.)$ representing the standard deviation function operator.
\end{itemize}
In practice only will be taken the vectors, values of $\mu_p$
with a $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.

\subsection{Datapack processing in the steady state paper test}
\label{subsec:numprocink}

In this test we have one data package that was filtered (\ref{fig:filtering2}) obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering2.eps}
\caption{Filtering of data package in the steady paper obtaining the mean and the deviation outcomes.}
\label{fig:filtering2}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical results} 
\label{sec:numerical}

In the analysis, the minimum grayscale value, 
it is fixed by the observable minimum light by the camera or the minimum speckle light intensity in the material analyzed.
By other side, the maximum grayscale value, 
it is fixed by the observable maximum light by the camera or the maximum speckle light intensity in the material analyzed.

@@

The activity level analysis in the ink drying process has as objective to analyze the behavior of speckle index in a  dynamic process,
in the context of a system that change your characteristic in time.

>>>>

\documentclass[review]{elsarticle}
\usepackage{comment}
\usepackage{url}
\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}
\usepackage[ruled]{algorithm2e}

@@

\bibliographystyle{elsarticle-num}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[svgnames]{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

@@

\title{Illumination Dependency in Dynamic Laser Speckle Analysis}

\author{Fernando Pujaico Rivera}
\author{Roberto Alves Braga, Jr.}

\address{Federal University of Lavras, Lavras, Brazil}
\fntext[myfootnote2]{201518201@posgrad.ufla.br}
\fntext[myfootnote1]{robertobraga@deg.ufla.br }

\begin{abstract}
We analyse how the frequency bands 
influence the independence 
of speckle index values from the level of illumination
%of the value speckle index from the level of illumination 
in a dynamic laser speckle analysis.
Specifically, 
we study how the temporal speckle deviation 
index is influenced by the use of three different frequency bands of the speckle signal.
Finally, it is shown how signals with high frequency components return values with greater independence of the level of illumination.
\end{abstract}

@@

\section{Introduction}
Dynamic laser speckle is a phenomenon that is used to monitor changes in laser illuminated samples. It can be measured by several different indices \cite{BSLTLBOOK}. These indices are associated to the level of changes and can be expressed by numerical and or graphical outcomes that can be affected by filtering during the image processing \cite{RIVERA2017144}. As an example, we have  the AVD \cite{avd} and 
IM \cite{ARIZAGA1999163} indices, that filter
the information present in the history of the speckle images like a first-order high pass filter with a cut-off in the middle
of the normalized frequency band.
For this reason, it is important to analyse how
the chosen frequency band alters the result of a selected index.
On the other hand, there is still a limitation in making a speckle analysis in the presence of inhomogeneous illumination, because
most biospeckle indices are influenced
by the use of a specific level of illumination \cite{REIS2016}.
The level of illumination can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or the very irregular surface present in a kefir \cite{kefir}.
It can also vary in accordance with the moisture present in a seed \cite{CARDOSO2011} due to the penetration of the light in the sample, or even when the colour of the sample varies, such as in the interface between cancerous and normal tissues \cite{BCB+:12a}.
This is the reason why there has been a continual search for an adequate index, despite the fact there are many indices presented in the literature \cite{BSLTLBOOK}, but still without a solution that is independent of the intensity of the illumination.
The move toward portable equipment \cite{Bra:17} reinforces the need to search for such methods and their relation with the illumination.
Thus, the present work aims to establish a relation between the frequency band used
and the speckle index; particularly in the dependence of
the temporal speckle deviation matrix \cite{Nothdurft:05} on the level of illumination.

\section{Description of the system}
\label{sec:description}

\subsection{Data for ink drying test}
\label{sec:descriptionink}
Fig.~\ref{fig:system} shows the system setup of the ink sample test during drying, where
a red laser was pointed at a layer of ink drying, monitored by a digital camera;
the images were collected receiving two different illumination levels, 
because the neutral density lens partially covers the laser beam \cite{REIS2016}.
The images were turned into data-sets:
the data was acquired with a sampling rate of $F_s=$ 12.5 hertz, with 
$N=400$ images collected per data-set. In all, there were collected $11$ data-sets 
(each one with the two different illumination levels) at minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$, $105$, $120$ and $150$ of the drying process.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system 
with the levels of illumination over a layer of ink drying.}
\label{fig:system}
\end{figure}
Two $250\times200$-pixel regions were selected from each image of the data-sets, 
corresponding to regions with two different levels of illumination, 
as shown with red lines in Fig.~\ref{fig:regions}; thus, 
in the right side of Fig.~\ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens,
 so that this side has low illumination, and
the left side has a high illumination.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}

\subsection{Data for steady state paper test}
\label{sec:descriptionpaper}
The test over steady state paper has a similar configuration, as seen in
Fig.~\ref{fig:system} with the absence of 
the neutral density lens.
The phenomenon observed was the variation of the speckle signal associated with  the speckle response of the material, 
the experimental setup of the camera, the resolution of the images and also to the mechanical noise; 
so that one data-set was collected sampled with a frequency of $F_s=$ 10 hertz. 
In all, there were $N=129$ 640$\times$480-pixel images collected.
Fig.~\ref{fig:meanpaper} represents
with a colour bar the result of calculating the temporal speckle mean matrix ($\mu$) using Eq.~(\ref{eq:cont1})
of Section~\ref{subsec:deviation}; thus, it is easy to see how the
laser illumination in piece of paper
%level of illumination by the laser of the paper 
has an elliptical form, being highest 
close to the top of the image.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall.eps}
\caption{Light intensity distribution in the paper test piece with highest illumination 
presented by red pixels and lowest by blue pixels.}
\label{fig:meanpaper}
\end{figure}

\section{Numerical analysis}
\label{sec:analysis}

The sampling frequency used in the analysis of each test 
was selected so as to achieve the best speed of sampling to observe 
an appropriate frequency band of each phenomenon.
The purpose of these two tests is to observe the behaviour of the indices in two cases: 
one with an homogeneous activity level in space and time, and another with a heterogeneous activity level.
Thus, given that the paper activity test and the ink drying test are independent events, 
without comparison between them, their sampling frequencies are different,
and selected according to the best behaviour of the curves, 
higher sampling frequencies being more appropriate for the ink drying test.

\subsection{Data filtering in three frequency bands}
\label{subsec:firfilters}
Each data-set or sub-set ($P_T$) went through a filter bank with 4 outputs. Each
one had a different type of processing. The first one was trivial: 
the data was passed through without change. This data-set is referred to as $P_T$. The other three outcomes
return  signals filtered in different frequency bands: 
the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
the band between $[\frac{1}{3},\frac{2}{3}]\frac{F_s}{2}$ (intermediate frequencies) and
the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies). This ultimately yields the data-sets 
$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in Fig.~\ref{fig:firfilters}.
The filtered data of the images were made using cascades
of two low-pass Finite Impulse Response (FIR) filters of order $32$, so that
$P_X+P_Y+P_Z=P_T$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.55\columnwidth]{firfilters.eps}
\caption{Filtering the data-sets.}
\label{fig:firfilters}
\end{figure}

\subsection{Temporal speckle deviation matrix}
\label{subsec:deviation}
The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05},
used to compare the results, was obtained from the $N$ images of the data-set $P$.
We designate each image matrix in $P$ as $\mathbf{I}_{k}$, $1\leq k \leq N$, 
with $k$ an integer that indicates whether the $k$-th image $\mathbf{I}_{k}$ in the data-set was used.
Thus, the following equation was used to get
the matrix $\sigma$:
\begin{equation}\label{eq:cont2}
\sigma  = \sqrt{ \frac{1}{N} \sum_{k=1}^{N} (\mathbf{I}_{k}-\mu)^2  },
\end{equation}
so that the matrix $\mu$ can be calculated as
\begin{equation}\label{eq:cont1}
\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k}.
\end{equation}
In these last two equations, all the operations are matricial, 
so that each element (i.e.\ pixel) $\mathbf{I}_{k}(i)$ in the matrix $\mathbf{I}_{k}$
should be processed with its  counterpart $\mathbf{I}_{k+1}(i)$ in the matrix $\mathbf{I}_{k+1}$.

Aditionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
of all elements in the matrix $\sigma$, with $<.>$ being the mean spatial operator.

@@

The Fujii matrix \cite{Fujii:87} is obtained from the $N$ images in $P$.
Similarly to Section~\ref{subsec:deviation}, 
we designate each image matrix in $P$ as $\mathbf{I}_{k}$, $1\leq k \leq N$.
Thus, the following equation is used to get the Fujii matrix:
\begin{equation}\label{eq:contFujii2}
Fujii  = \frac{1}{N-1} \sum_{k=1}^{N-1} \frac{|\mathbf{I}_{k}-\mathbf{I}_{k+1}|}{\mathbf{I}_{k}+\mathbf{I}_{k+1}}.
\end{equation} 
The mean value of the Fujii matrix can be defined as $\overline{Fujii}=<Fujii>$, the mean value
of all elements in the $Fujii$ matrix.

The Fujii method is an attempt to eliminate 
the dependence of a speckle index on the level 
of illumination. For this purpose, the method defines the index as the mean value of the  first-order high pass FIR filter 
$\mathbf{I}_{k}-\mathbf{I}_{k+1}$, similarly to the  AVD index \cite{avd};
but in the Fujii method the values are corrected using an approximation of the mean value of the intensity, 
$\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
This aspect of the calculation is the strong point of the method,
because the method assumes that the increase in the dynamic range of the speckle 
light ($\mathbf{I}_{k}-\mathbf{I}_{k+1}$) 
will be linear in proportion with the increase in the laser light ($\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$).
This means that the method already uses the high frequency components
of the speckle signal, 
and discards those of low frequency, 
in addition to attempting to correct or  normalize the values of the index.
It is for these reasons that it has an acceptable performance in
eliminating or decreasing the dependence of the index on the level of intensity of the laser light.

Additionally, there is defined the matrix $Fujii_{\alpha}$, 
as the index of the filtered version of $P$ in the frequency band $\alpha$,  using the following equation:
\begin{equation}\label{eq:contFujii3}
Fujii_{\alpha}  = \frac{1}{N-1} \sum_{k=1}^{N-1} \frac{|\mathbf{(I_{\alpha})}_{k}-\mathbf{(I_{\alpha})}_{k+1}|}{\mathbf{I}_{k}+\mathbf{I}_{k+1}}.
\end{equation}
It is important to stress that the numerator of this equation 
uses the signal in the matrices $\mathbf{(I_{\alpha})}_{k}$, which are filtered versions in the frequency band $\alpha$,
of the matrix $\mathbf{I}_{k}$.
On the ohter hand, the denominator uses the signal $\mathbf{I}_{k}$, which employs the complete frequency band.
This modification was implemented because the numerator, in the calculation, 
represents or tries be the mean value of the intensity of the speckle light, 
and its value tends to zero in frequency bands without 0 hertz components.

\subsection{Data processing in the ink drying test}
\label{subsec:numprocink}

There are two levels of illumination in the ink drying regions.
For this reason, we  separated each data-set into two sub-sets
(high and low illumination), representing each one of the regions shown in Fig.~\ref{fig:regions}.
These sub-sets were filtered,
obtaining $P_T$, $P_X$, $P_Y$ and $P_Z$, which were used to obtain
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data-sets.}
\label{fig:filtering}
\end{figure}
the temporal speckle deviation matrix and the 
temporal speckle deviation indices $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$.

\subsection{Statistical analysis of relation between the matrices $\sigma$ and $\mu$}
\label{subsec:statistical}
We define $\sigma_i$ and $\mu_i$
as the values in the $i$th position in $\sigma$  
and $\mu$, respectively. We also define $\mu_p$
as the value of any element of $\mu$.
We also define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
as the set of all values of $\sigma_i$  given that $\mu_i\equiv\mu_p$.
We thus obtain the vectors $L_p$, $\sigma_p$ and
$e_p$ using all the values $\mu_p$:
\begin{itemize}
 \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  where $L_p(\mu_p)$ is the number of elements
 in the set $S_{\mu_p}$ and $card(.)$ means the cardinality of a set.
 \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, where $\sigma_p(\mu_p)$
 is the mean of the elements in the set $S_{\mu_p}$, with $mean(.)$ denoting the mean value operator.
 \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, where $e_p(\mu_p)$
 is the standard  deviation of the elements in the set $S_{\mu_p}$, with $std(.)$ denoting `standard deviation'.
\end{itemize}
In practice, the vectors will only be taken using the values of $\mu_p$
with $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.

\subsection{Data processing in the steady state paper test}
\label{subsec:numprocink}

In this test we have one data-set that was filtered (\ref{fig:filtering2}) 
obtaining $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
temporal speckle deviation matrix, as can be seen in Fig.~\ref{fig:filtering2}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering2.eps}
\caption{Filtering of the steady paper data-set, obtaining the mean and the deviation.}
\label{fig:filtering2}
\end{figure}

\section{Numerical results} 
\label{sec:numerical}

In the analysis, the minimum greyscale value 
is fixed by the minimum light observable by the camera or the minimum speckle light intensity in the material analysed.
The maximum greyscale value
is fixed by the maximum light observable by the camera or the maximum speckle light intensity in the material analysed.

@@

The activity level analysis in the ink drying process has as objective to analyse 
the behaviour of the speckle index in a  dynamic process,
in the context of a system that changes its characteristics over time.

In Fig.~\ref{fig:numerical}, we can see the result of processing 
 the data for the ink drying test under the dynamic laser speckle index (DLSI) in two areas with 
different level of illumination. Fig.~\ref{fig:allink}
represents $\bar{\sigma}_T$ for two light intensity levels. It was obtained using $P_T$
over time, with the complete frequency bands.
Fig.~\ref{fig:stdxink}
represents $\bar{\sigma}_X$ for two light intensity levels, using $P_X$
over time, with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$\ Hz.
Fig.~\ref{fig:stdyink}
represents $\bar{\sigma}_Y$ for two light intensity levels, using $P_Y$
over time, with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
Fig.~\ref{fig:stdzink}
represents $\bar{\sigma}_Z$ for two light intensity levels, using $P_Z$
over time, with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-all.eps}
	\caption{$\bar{\sigma}_T$ over time.}
        \label{fig:allink}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandx.eps}
	\caption{$\bar{\sigma}_X$ over time.}
        \label{fig:stdxink}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandy.eps}
	\caption{$\bar{\sigma}_Y$ over time.}
        \label{fig:stdyink}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandz.eps}
	\caption{$\bar{\sigma}_Z$ over time.}
        \label{fig:stdzink}
    \end{subfigure}

\caption{Numerical results for the ink drying test.}\label{fig:numerical}
\end{figure}

As can be seen, when we analysed the index over the complete frequency band (Fig.~\ref{fig:allink}),
the two different levels of illumination provided different results, high on the left 
side of Fig.~\ref{fig:regions} and low on the right. This 
indicates a positive influence of the level of illumination on the index.
On the other hand, %Figs~\ref{fig:stdxink}, 
\ref{fig:stdyink} and \ref{fig:stdzink}
show how the index under different levels of illumination are similar when compared at the same frequency component,
with the greatest similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
